Inverse Problems --- Example Sheet 2

### 2020-11-14 distribution_theory/C1.tex
worked on some example sheets, updated msm and topics summaries (todo: dist and inv prob)
updated distribution theory, still struggling with topics ugh
it's weekend, party time

\subsection{Limits in $\DD'(X)$}
\begin{definition}
    We say that a sequence $(u_m) \subseteq \DD'(X)$ converges to $u \in \DD'(X)$ and write $u_m \to u$ if 
    \[
    \ang{u_m, \phi} \to \ang{u, \phi} \quad\text{for all $\phi \in \DD(X)$}. 
    \]
\end{definition}

@@

\subsection{Density of $\DD(\RR^n)$ in $\DD'(\RR^n)$}
\begin{lemma}
	If $u \in \DD'(\RR^n)$ and $\phi, \psi \in \DD(\RR^n)$, then
	\[
	(u * \phi) * \psi = u * (\phi * \psi). 
	\]
\end{lemma}

@@

@@

	Note that $\ang{u, \phi} = (u * \refl\phi)(0)$ by definition. Now, take any $\theta \in \DD(\RR^n)$, then we have

>>>>

\subsection{Limits in the distribution space}
\begin{definition}
    We say that a sequence $(u_m) \subseteq \DD'(X)$ converges to $u \in \DD'(X)$ and write $u_m \to u$ if 
    \[
    \ang{u_m, \phi} \to \ang{u, \phi} \quad\text{for all $\phi \in \DD(X)$}. 
    \]
\end{definition}

@@

\subsection{Density of test functions in distribution space}
\begin{lemma} \label{lem:convolution_associative}
	If $u \in \DD'(\RR^n)$ and $\phi, \psi \in \DD(\RR^n)$, then
	\[
	(u * \phi) * \psi = u * (\phi * \psi). 
	\]
\end{lemma}

@@

We will use the following trick many times:
\begin{proposition}
	For any $u \in \DD'(\RR^n), \phi \in \DD(\RR^n)$ we have $\ang{u, \phi} = (u * \refl\phi)(0)$. 
\end{proposition}

\begin{proof}
	We have $(u * \refl\phi)(0) = \ang{u, \tau_0 \phi} = \ang{u, \phi}$. 
\end{proof}
For example, from this trick it follows that if $u * \phi = 0$ for all $\phi$, then $u = 0$.

@@

	Now, take any $\theta \in \DD(\RR^n)$, then we have

### 2020-11-14 distribution_theory/C4.tex
it's weekend, party time

>>>>

As a guess to construct fundamental solutions, we can use the Fourier transform: we have
\begin{align*}
	p(D) E = \delta_0 &\implies p(\lambda) \hat E = 1 \implies \hat E = \frac{1}{p(\lambda)}  \\
	&\implies \ang{E, \phi} = \ang{E,\frac{1}{(2\pi)^n} \FF[\refl{\FF[\phi]}]} = \frac{1}{(2\pi)^n}\ang{\hat E, \refl{\FF[\phi]}} =\frac{1}{(2\pi)^n} \int \frac{\hat\phi(-\lambda)}{p(\lambda)} \dd{\lambda}. 
\end{align*}

Indeed, one can check that this $E$ ``works'', but the problem is that we have no guarantee that $E \in \DD'(\RR^n)$, since $p(\lambda)$ may cause problems at its roots. To circumvent this, we have to use a construction called \emph{H\"ormander's staircase}.
For this, we will first need a lemma. For $x \in \RR^n$, we will write $x = (x', x_n)$ with $x' \in \RR^{n-1}$. 
\begin{lemma}
	For each $\phi \in \DD(\RR^n)$ and $\lambda' \in \RR^{n-1}$, the function $z \mapsto \hat\phi(\lambda', z)$ is analytic in $z\in\CC$. Furthermore, for each $m \in \NN_0$ there exists constants $c_m, \delta > 0$ (independent of $\lambda'$) such that
	\[
	\abs{\hat\phi(\lambda', z)} \leq c_m(1 + \abs{z})^{-m} e^{\delta \abs{\Im z}}. 
	\] 
\end{lemma}

\begin{proof}
	By definition of the Fourier transform and Fubini's theorem, we have
	\[
	\hat\phi(\lambda', z) = \int e^{-i\lambda' \cdot x'} \int e^{-i z x_n} \phi(x', x) \dd{x_n} \dd{x'}. 
	\]
	It is easily seen that this function is smooth in $z$ and satisfies the Cauchy-Riemann equations, which means it is analytic.

	Integrating by parts we find
	\begin{align*}
		\abs{z^m \hat\phi(\lambda', z)} &= \abs{\int e^{-i\lambda' \vdot x'} \int \qty(i \pdv{x_n})^m e^{-i z x_n} \phi(x', x_n) \dd{x_n} \dd{x'} } \\
		&= \abs{\int e^{-i\lambda' \vdot x'} \int e^{-i z x_n} \qty(\pdv[m]{x_n} \phi(x', x_m)) \dd{x_m} \dd{x'}} \\
		&\leq \iint \abs{e^{-iz x_n}} \cdot \abs{\pdv[m]{x_n} \phi(x', x_n)} \dd{x_n} \dd{x'} \\
	&\leq c_m e^{\delta \abs{\Im z}}, 
	\end{align*}
	where $\delta$ is chosen such that $\phi(x', x_n) = 0$ if $\abs{x_n}> \delta$. 
\end{proof}

Now, we can prove the main theorem of this section, which \emph{almost} gives an explicit construction for a fundamental solution:
\begin{theorem}
	Every nonzero constant-coefficient partial differential operator has a fundamental solution. 
\end{theorem}

\begin{proof}
	By rotating our coordinate axes, we can assume $p$ takes the form
	\[
	p(\lambda', \lambda_n) = \lambda_n^M + \sum_{m=1}^{M-1} a_m(\lambda') \lambda_n^m, 
	\]
	(??) (i.e., we simply write $p$ as a polynomial in $\lambda_n$). Fix $\mu' \in \RR^{n-1}$, then we can write
	\[
	p(\mu', \lambda_n) = \prod_{i=1}^M (\lambda_n - \tau_i(\mu')), 
	\]
	where the $\tau_i$ are the roots of the polynomial $\lambda_n \mapsto p(\mu', \lambda_n)$. Now, by the pigeonhole principle, there exists a horizontal line $\Im\lambda_n = c(\mu')$ in the region $\abs{\Im\lambda_n} \leq M + 1$ such that
	\[
	\abs{\lambda_n - \tau_i(\mu')} > 1 \quad\text{on $\Im\lambda_n = c(\mu')$} \quad (i = 1, \dotsc, m)
	\]
	Therefore, on $\Im(\lambda_n) = c(\mu')$ we have $\abs{p(\lambda', \lambda_n)} \ges 1$.

	Since roots of a polynomial vary continuously with its coefficients, we can use the same horizontal line $\Im\lambda_n = c(\mu')$ for all $\lambda'$ in a (small) neighbourhood $N(\mu')$ of $\mu'$. We can cover all of $\RR^{n-1}$ with such neighbourhoods, and by the Heine-Borel theorem, we can extract a locally finite subcover $N_1 = N(\mu_1'), N_2 = N(\mu_2'), \dotsc$. Furthermore, we can modify these neighbourhoods so that they are disjoint by defining 
	\[
	\Delta_i = N_i \setminus \qty(\bigcup_{j=1}^{i-1} \overline{N_j}). 
	\]
	The $\Delta_i$ are all open, disjoint, and satisfy $\RR^{n-1} = \cup_i \overline{\Delta_i}$.
	Now we define
	\[
	\ang{E, \phi} \ceq \frac1{(2\pi)^n} \sum_{i=1}^\infty \int_{\Delta_i} \int_{\Im\lambda_n = c_i} \frac{\hat\phi(-\lambda' - \lambda_n)}{p(\lambda', \lambda_n)} \dd{\lambda_n} \dd{\lambda'}. 
	\]
	In ES3, it is shown that $E \in \DD'(\RR^n)$. Furthermore, we have
	\begin{align*}
		\ang{p(D)E, \phi} &= \ang{E, p(-D)\phi} = \frac1{(2\pi)^n} \sum_{i=1}^\infty \int_{\Delta_i} \int_{\Im\lambda_n = c_i} \frac{p(\lambda', \lambda_n)}{p(\lambda', \lambda_n)} \hat\phi(-\lambda' - \lambda_n) \dd{\lambda_n} \dd{\lambda'} \\
		&= \frac1{(2\pi)^n} \sum_{i=1}^\infty \int_{\Delta_i} \int_{\Im\lambda_n = c_i}  \hat\phi(-\lambda' - \lambda_n) \dd{\lambda_n} \dd{\lambda'}  \\
		&\overset\star= \frac1{(2\pi)^n} \sum_{i=1}^\infty \int_{\Delta_i} \int_{\Im\lambda_n = 0}  \hat\phi(-\lambda' - \lambda_n) \dd{\lambda_n} \dd{\lambda'} = \frac1{(2\pi)^n} \int_{\RR^n} \hat\phi(-\lambda) \dd{\lambda} = \phi(0).
	\end{align*} 
by the Fourier inversion theorem. Here, $\star$ follows from the Cauchy's theorem and the previous lemma ($\hat\phi$ decays rapidly in the horizontal direction, so taking a contour integral over a rectangle and letting the vertical side go to infinity shows that the integral over $\Im \lambda_n = c_i$ equals the integral over $\Im\lambda_n = 0$). We conclude that $p(D)E = \delta_0$. 
\end{proof}

Note that the only nonconstructive part of the theorem is the extraction of a locally finite subcover of the neighbourhoods $N(\mu')$.

\subsection{Structure theorem for distributions of compact support}
In this section, we will prove that every $u \in \EE'(X)$ can be written as a finite sum $u = \sum_\alpha \pt^\alpha f_\alpha$ where the $f_\alpha$ are continuous. The theorem generalises to $u \in \DD'(X)$ (the sum can then be infinite, but locally finite), but we will not prove this, since it requires the use of partitions of unity.

We start with a lemma:
\begin{lemma}
	For $u \in \EE'(\RR^n)$, the Fourier transform $\hat u \in \SS'(\RR^n)$ can be identified with the smooth (analytic) function $\lambda \mapsto \ang{u(x), e^{-i\lambda\vdot x}}$, which we will denote $\hat u(\lambda)$. 
\end{lemma}

\begin{proof}
	We will first prove the density of $\DD(\RR^n)$ in $\SS(\RR^n)$. 
	Fix $\phi \in \SS(\RR^n)$ and $\chi \in \DD(\RR^n)$ with $\chi = 1$ on $\norm{x}\leq1$ and $\chi = 0$ on $\norm{x}>2$. Define $\phi_m \in \DD(\RR^n)$ by $\phi_m(x) \ceq \phi(x) \chi(x/m)$. We will show that $\phi_m \to \phi \in \SS(\RR^n)$.

	For each pair of multi-indices $\alpha, \beta$, we have
	\begin{align*}
		\norm{\phi - \phi_m}_{\alpha, \beta} &= \norm{x^\alpha D^\beta( \phi - \phi_m)}_\infty = \norm{x^\alpha D^\beta(\phi \cdot \qty{1 - \chi(x/m)})} \\
		&= \norm{x^\alpha \sum_{\gamma \leq \beta} \binom\beta\gamma (D^\gamma\phi)(x) \cdot D^{\beta - \gamma} (1 - \chi(x/m))}. 
	\end{align*}
	For $\gamma \neq \beta$, the derivative $D^\gamma\phi$ is bounded uniformly while the derivative $D^{\beta - \gamma} (1 - \chi(x/m))$ will converge uniformly to 0 since it will have at least one factor $1/m$. For $\gamma = \beta$, we have
	\[
	\norm{x^\alpha (1 - \chi(x/m)) D^\beta\phi}_\infty \leq \sup_{\norm{x} > M} \norm{x^\alpha D^\beta\phi} \to 0,
	\]
	since $D^\beta\phi$ decays rapidly. We conclude that $\norm{\phi - \phi_m}_{\alpha, \beta} \to 0$, and therefore that $\phi_m \to \phi$ in $\SS(\RR^n)$.

	Now, by a Riemann sum argument (like the one we have used in \cref{lem:convolution_associative}) we have
	\begin{align*}
		\ang{\hat u, \phi_m} &= \ang{u, \hat \phi_m} = \ang*{u(x), \int e^{-i\lambda\vdot x} \phi_m(\lambda) \dd{\lambda}} 
		\overset\star= \int \ang{u(x), e^{-i\lambda\cdot x}} \phi_m(\lambda) \dd{\lambda}, 
		\end{align*}
	where $\star$ is the Riemann sum argument (here, we need that $\phi_m$ has compact support).  Now, since $u \in \EE'(\RR^n)$, there exists a compact $K$ and constants $C', N > 0$ such that
	\[
	\abs{\ang{u(x), e^{-i\lambda\cdot x}}} \leq C' \sum_{\abs{\alpha} \leq N} \sup_K \abs{D_x e^{-i\lambda\cdot x}} \leq C \ang{\lambda}^N, 
	\]
	so $\lambda \mapsto \ang{u(x), e^{-i\lambda\cdot x}}$ is polynomially bounded, and therefore we can use the dominated convergence theorem to conclude
	\[
	\ang{\hat u, \phi} = \lim_{n\to\infty} \ang{\hat u, \phi_m} = \lim_{n\to\infty} \int \ang{u(x), e^{-i\lambda\cdot x}} \phi_m(\lambda) \dd{\lambda} = \int \ang{u(x), e^{-i\lambda\cdot x}} \phi(\lambda) \dd{\lambda}, 
	\]
	which proves that $\hat u$ can be identified with the function $\hat u(\lambda) = \ang{u(x), e^{-i\lambda\vdot x}}$. 
\end{proof}

Furthermore, it is clear that for $u \in \EE'(\RR^n)$, we have 
\begin{equation} \label{eq:fourier_estimate}
	\abs{\hat u(\lambda)} \leq C \sum_{\abs{\alpha} \leq N} \sup_K \abs{\pt^\alpha_x e^{-i\lambda x}} \les \ang{\lambda}^N.
\end{equation}

\begin{theorem}[Structure theorem]
	For $u \in \EE'(X)$, there exists a finite collection $\qty{f_\alpha} \subseteq C(X)$ with $\supp(f_\alpha) \subseteq X$ such that $u = \sum_\alpha \pt^\alpha f_\alpha$ in $\EE'(X)$. 
\end{theorem}

\begin{proof}
	Fix $\rho \in \DD(X)$ with $\rho = 1$ on a neighbourhood of $u$, then we can extend $u$ to $\EE'(\RR^n)$ by setting $\ang{u, \phi} \ceq \ang{u, \rho\phi}$ (note that $\rho\phi \in \DD(X)$ for all $\phi \in \EE(\RR^n)$). Since $\rho\phi \in \SS(\RR^n)$, we know there exist $\psi \in \SS(\RR^n)$ such that
	\[
	\rho\phi = \FF[\FF[\psi]] = (2\pi)^n \refl\psi, 
	\]
	and therefore
	\[
	\ang{u, \rho\phi} = \ang{u, \FF[\FF[\psi]]} = \ang{\hat u, \hat\psi}. 
	\]
	Using the Laplacian $\Delta = \sum_i \pt^i \pt^i$, we can write for any $m \in \NN$
	\[
	\hat\psi = \ang{\lambda}^{-2M} \FF\qty[(1 - \Delta)^M \psi],
	\]
	since $\FF\qty[(1 - \Delta)^m \psi] = (1 + \norm{\lambda}^2)^m \hat\psi = \ang{\lambda}^{2M}\hat\psi$.

	Plugging this back into our previous equations, we have
	\begin{equation} \label{eq:fourier_laplace}
		\ang{\hat u, \hat\psi} = \ang{\hat u, \ang{\lambda}^{-2M} \FF[(1 - \Delta)^M \psi]} = \ang*{\FF[\hat u \ang{\lambda}^{-2M}], (1 - \Delta)^M \psi}.
	\end{equation}
Now, by \cref{eq:fourier_estimate}, we have $\abs{\hat u(\lambda)} \les \ang{\lambda}^N$, so we can choose $M$ large enough such that $\hat u(\lambda) \cdot \ang{\lambda}^{-2M} \in L^1(\RR^n)$, and by the dominated convergence theorem, the function
\[
f(x) = \frac1{(2\pi)^n} \int e^{-i\lambda \vdot x} \ang{\lambda}^{-2M} \hat u(\lambda) \dd{\lambda} 
\]
is continuous, and it is easily checked that $(2\pi)^n \refl f = \FF[\ang{\lambda}^{2M} \hat u(\lambda)]$.

Using the fact that $(2\pi)^n \refl\psi = \rho\phi$, and going back to \cref{eq:fourier_laplace} we see
\[
\ang{u, \rho\phi} = \ang{(2\pi)^n \refl f, (1 - \Delta)^M \psi} = \ang{\refl f, (1 -\Delta)^M \refl{(\rho\phi)}} = \ang{f, (1 - \Delta)^M (\rho\phi)}, 
\]
where the last step follows from the fact that the Laplacian is reflection invariant.

Expanding the derivatives using the Leibniz rule yields
\[
(1 -\Delta)^M (\rho\phi) = \sum_\alpha (-1)^{\abs{\alpha}} \rho_\alpha \pt^\alpha\phi
\]
for suitable $\rho_\alpha \in \DD(X)$, and therefore we have
\[
\ang{u, \phi} = \sum_\alpha \ang{f, (-1)^{\abs{\alpha}} \rho_\alpha \pt^\alpha\phi} = \ang*{\sum_\alpha \pt^\alpha(\rho_\alpha f), \phi},
\]
so $u = \sum_\alpha \pt^\alpha(\rho_\alpha f) = \sum_\alpha \pt^\alpha f_\alpha \in \EE'(\RR^n)$, where $f_\alpha$ is continuous and $\supp(f_\alpha) = \supp(\rho_\alpha f) \subseteq X$. 
\end{proof}

There also exist nonconstructive proofs for the previous theorem using Hahn-Banach.

### 2020-11-14 inverse_problems/inverse_ES2.tex
I actually UNDERSTOOD topics
it's weekend, party time

\title{Inverse Problems --- Example Sheet 2} % subject
\author{Lucas Riedstra}
\date{18 November 2020} % date

@@

\item 
\end{enumerate}
\end{solution}
\end{document}

>>>>

\title{Inverse Problems --- Example Sheet 2} % subject
\author{Lucas Riedstra}
\date{16 November 2020} % date

@@

\item Let $f \in L^1(\Omega) \setminus \BV(\Omega)$, then clearly $\pt \TV(f) = \emptyset$. Now suppose $f \in \BV(\Omega)$.  It is known that the dual of $L^1(\Omega)$ is $L^\infty(\Omega)$. Therefore, we have for $p \in L^\infty(\Omega)$ that 
\begin{align*}
	p \in \pt \TV(f) &\iff \TV(g) \geq \TV(f) + \int_{\Omega} p(x) (g - f)(x) \dd{x} \ \forall g \in L^1(\Omega)
\end{align*}
(??)
\end{enumerate}
\end{solution}

\begin{question}
	Let $\UU$ be a Banach space and let $E \colon \UU\to \rext$ be proper, lower semi-continuous and convex. Then the \emph{Fenchel conjugate} or \emph{convex conjugate} of $E$ is defined to be the mapping $E^* \colon \UU^* \to \RR$ with
	\[
	E^*(v) \ceq \sup_{u \in \UU} \qty{\ang{v, u} - E(u)}. 
	\]
	\begin{enumerate}[(a)]
		\item Compute the convex conjugates of the following functionals.
		\begin{enumerate}[(i)]
			\item $E(u) = \norm{u}_\UU$ for a Banach space $\UU$,
			\item $E(u \mid f) = \sum_{i=1}^n u_i \log(\frac{u_i}{f_i})$, where $f \in \RR^n_{>0}$ is a positive vector and $u \in \RR^n$. What is the effective domain of $E$? 
		\end{enumerate}
	\item Let $E \colon \UU\to\rext$ be a proper, lower semi-continuous and convex functional. Show that
	\[
	p \in \pt E(u) \iff u \in \pt E^*(p)
	\]
	for all $u, p \in \UU$.

	\emph{Hint:} You may exploit the fact that under the stated assumptions $E = E^{**}$ holds true. 
	\end{enumerate}
\end{question}

\begin{solution}
	\begin{enumerate}[(a)]
		\item \begin{enumerate}[(i)]
			\item We have
			\[
			E^*(v) = \sup_{u \in \UU} \qty(\ang{v, u} - \norm{u}). 
			\]
			Suppose $\ang{v, u^*} - \norm{u^*} = \xi > 0$ for some $u^*$. Then we have for $\alpha > 0$ that
			\[
			\ang{v, \alpha u^*} - \norm{\alpha u^*} = \alpha \qty(\ang{v, u^*} - \norm{u^*}) = \alpha\xi, 
			\]
			and therefore clearly $E^*(v) = \infty$.

			On the other hand, if $\ang{v, u} - \norm{u}\leq0$ for all $u$, then the supremum is attained in $u = 0$ with value $0$, and therefore $E^*(v) = 0$.

			We see that
			\begin{align*}
				&\ang{v, u^*} - \norm{u^*} > 0 &\text{for some $u^* \in \UU$}; \\
				&\iff \ang{v, u^*} > \norm{u^*} &\text{for some $u^* \in \UU$}; \\
				&\iff \norm{v}_{\UU^*} > 1. 
			\end{align*}
		We conclude that
		\[
		E^*(v) = \chi_\qty{\norm{v} \leq 1} = \begin{cases}
			0 &\text{if $\norm{v} \leq 1$}, \\ \infty &\text{else.}
		\end{cases}
		\]

		\item Suppose first that $p \in \pt E(u)$. Then we have
		\begin{align*}
&\phantom{\implies}	p \in \pt E(u) \\
&\implies E(v) \geq E(u) + \ang{p, v - u} &\text{for all $v$} \\
&\implies \ang{p, u} - E(u) \geq \ang{p, v} - E(v) &\text{for all $v$} \\
&\implies \ang{p, u} - E(u) \geq \sup_v \qty(\ang{p, v} - E(v)) = E^*(p) \\
&\implies \ang{p, u} - E(u) + \ang{q - p, u} \geq E^*(p) + \ang{q - p, u} &\text{for all $q$} \\
&\implies \ang{q, u} - E(u) \geq E^*(p) + \ang{q - p, u} &\text{for all $q$} \\
&\implies \sup_v \qty(\ang{q, v} - E(v)) \geq E^*(p) + \ang{q - p, u} &\text{for all $q$} \\
&\implies E^*(q) \geq E^*(p) + \ang{q -p, u} &\text{for all $q$} \\
&\implies u \in \pt E^*(p). 
		\end{align*}
	Now, for the reverse implication, note that by what we just proved we have
	\[
	u \in \pt E^*(p) \implies p \in \pt E^{**}(u) \iff p \in \pt E(u), 
	\]
	which proves the claim.
		\end{enumerate}
	\end{enumerate}
\end{solution}

\begin{question}
	Let $u, v \in \UU$ and $p \in \pt J(v)$. Recall that the Bregman distance of $J$ at $u, v$ is defined as
	\[
	D_J^p(u, v) \ceq J(u) - J(v) - \ang{p, u - v}.
	\]
	\begin{enumerate}[(a)]
		\item Show that Bregman distances are non-negative. 
		\item Show that Bregman distances may not be symmetric, i.e., there exists a $J$ and $u, v \in \UU$ with $p \in \pt J(v), q \in \pt J(u)$ such that $D_J^p(u, v) \neq D_J^q(v, u)$.
		\item Show that a vanishing Bregman distance may not imply that the two arguments are the same. What if $J$ is strictly convex?
	\end{enumerate}

\end{question}

\begin{proof}
	\begin{enumerate}[(a)]
		\item Since $p \in \pt J(v)$, we have $J(u) \geq J(v) + \ang{p, u - v}$, or equivalently $J(u) - J(v) - \ang{p, u- v} \geq 0$.

		\item Let $\UU = \RR$, $J(x) = \abs{x}$, and choose $u = 0, v = 1$ and $p = 1, q = 0$. Then 
		\[
		D^p_J(u, v) = -1 - (-1) =  0 \quad\text{and}\quad D^q_J(v, u) = 1. 
		\]

		\item In the previous part we had an example $J(x)= \abs{x}, u = 0, v = 1, p = 1$, where $D_J^p(u, v) = 0$ while $u \neq v$.

		Suppose that $J$ is strictly convex and that $u \neq v$ but $D_J^p(u, v) = 0$, so $J(u) = J(v) + \ang{p, u-v}$. Then we have for all $t \in (0, 1)$ that 
		\begin{align*}
			J(v) + \ang{p, (1-t)(u-v)} &= J(v) + \ang{p,  \qty(tv + (1-t)u) -v} \\
			&\overset\star\leq J(tv + (1-t) u) \\
			&< t J(v) + (1-t) J(u) \\
			&= t J(v) + (1-t) \qty(J(v) + (1-t)\ang{p, u-v}) \\
			&= J(v) + \ang{p, (1-t)(u-v)}, 
		\end{align*}
	a contradiction (here $\star$ follows from $p \in \pt J(v)$). We conclude that, if $J$ is strictly convex, the Bregman distance does satisfy $u \neq v \implies D_J^p(u, v) > 0$.

	\end{enumerate}
\end{proof}

\begin{question}
	Recall that a function $J \colon \UU\to \rext$ is called absolutely one-homogeneous if $J(\lambda u) = \abs{\lambda} J(u)$ for all $\lambda \in \RR, u \in \UU$. Let $J$ be convex, proper, l.s.c.\ and absolutely one-homogeneous. 
	\begin{enumerate}[(a)]
		\item Show that $p \in \pt J(v)$ if and only if $p \in \pt J(0)$ and $J(v) = \ang{p, v}$.
		Therefore, 
		\[
		D_J^p(u, v) = J(u) - \ang{p, u}. 
		\]
		Show that
		\[
		\pt J(0) = \bigcup_{u \in \UU} \pt J(u). 
		\]

		\item Show that the Bregman distances associated with absolutely one-homogeneous functionals fulfill the triangle inequality in the first argument, i.e., for all $u, v, w \in \UU$ and $p \in \pt J(w)$ there is
		\[
		D_J^p(u + v, w) \leq D_J^p(u, w) + D_J^p(v, w). 
		\]

		\item Show that the convex conjugate $J^*(\cdot)$ is the characteristic function of the convex set $\pt J(0)$. Compare this to the results of Exercise 2(a)(i). 
	\end{enumerate}
\end{question}

\begin{proof}
	It is clear that $J(0) = 0$. 
	\begin{enumerate}[(a)]
		\item Suppose $p \in \pt J(v)$. Then we have $J(u) \geq J(v) + \ang{p, u - v}$ for all $u$, which we can rewrite as $J(u) - \ang{p, u} \geq J(v) - \ang{p, v}$. Plugging in $u = 0$ we obtain $J(v) - \ang{p, v} \leq 0$, but plugging in $u = 2v$ we obtain
		\[
		2 \qty(J(v) - \ang{p, v}) = J(2v) - \ang{p, 2v} \geq J(v) - \ang{p, v} \implies J(v) - \ang{p, v} \geq 0, 
		\]
		so we conclude $J(v) - \ang{p, v} = 0$ or $J(v) = \ang{p, v}$. 	
		This also implies that
		\[
		J(u) \geq \ang{p, u} \text{ for all $u$} \implies p \in \pt J(0). 		
		\]

		Conversely, if $p \in \pt J(0)$ and $J(v) = \ang{p, v}$, then for all $u$ we have
		\[
		J(u) \geq \ang{p, u} + (J(v) - \ang{p, v}) \implies p \in \pt J(v).
		\]
		This concludes the first claim.

		From this claim, it follows that $\pt J(u) \subseteq \pt J(0)$ for all $u \in \UU$, and therefore trivially $\pt J(0) = \cup_u \pt J(u)$.

		\item Note that we have
		\[
		J(u+v) = 2 J\qty(\frac12u + \frac12 v) \leq 2\qty(\frac12 J(u) + \frac12J(v)) = J(u) + J(v), 
		\]
		and therefore
		\[
		D_J^p(u+v, w) = J(u+v) - \ang{p, u +v} \leq J(u) + J(v) - \ang{p, u} - \ang{p, v} = D_J^p(u, w) + D_J^p(v, w). 
		\]

		\item We can reason analogously to 2(a)(i): we have
		\[
		J^*(v) = \sup_{u \in U} (\ang{v, u} - J(u)).
		\]
		Suppose that $v \notin \pt J(0)$, i.e., $\ang{v, u^*} - J(u) = \xi > 0$ for some $u^*$. Then we have for all $\lambda > 0$ that 
		\[
		\ang{v, \lambda u^*} - J(\lambda u^*) = \lambda \xi, 
		\]
		and letting $\lambda \to\infty$ shows $J^*(v) = \infty$.

		On the other hand, suppose that $v \in \pt J(0)$, i.e., $\ang{v, u} - J(u) \leq 0$ for all $u$. Then the supremum is attained in $u = 0$ and therefore we have $J^*(v) = 0$.

		It follows that $J^*(v) = \pt J(0)$, which is indeed also what we saw in 2(a)(i), since the subdifferential of the norm at 0 is exactly $\qty{v \in \UU^* : \norm{v}_{\UU^*} \leq 1}$. 
	\end{enumerate}
\end{proof}
\end{document}
